\documentclass[a4paper,12pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%\usepackage[T2A]{fontenc} % jei yra kirilica
\usepackage[hmargin={30mm,15mm},vmargin={20mm,20mm},bindingoffset=0mm]{geometry}
\usepackage[onehalfspacing]{setspace}
\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue, unicode]{hyperref}

%\parindent=7mm
\renewcommand{\refname}{Literatūros sąrašas} % article
%\renewcommand{\bibname}{Literatūros sąrašas} % report
\renewcommand{\contentsname}{Turinys}
\usepackage[T1]{fontenc} 

% Lukas paketai
\usepackage{booktabs}% http://ctan.org/pkg/booktabs
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{setspace}
\usepackage{color}
\usepackage{placeins}
\usepackage{booktabs}% http://ctan.org/pkg/booktabs
\usepackage{tabularx}% http://ctan.org/pkg/tabularx
\usepackage[parfill]{parskip}
\usepackage[unicode]{hyperref}
\usepackage{hyperref}
\usepackage{tocloft}
\usepackage{graphicx}
\newcommand\AtPageUpperRight[1]{\AtPageUpperLeft{%
   \makebox[\paperwidth][r]{#1}}}
\usepackage[dotinlabels]{titletoc}
\usepackage[capposition=top]{floatrow}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}
\usepackage{secdot}




\begin{document}
\graphicspath{ {/} }

\renewcommand{\cftdot}{.}	
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

\thispagestyle{empty} % nerasomas psl. nr


\begin{center}
 Curriculum Vitae\\
\textbf{Lukas Tutkus} \\

\vspace{5cm}

\textbf{Address}
\begin{itemize}
	\item Didlaukio g. 59, Vilnius, 08302, Lietuva. 
	\item Anykščių vns., Anykščiai, 29159, Lietuva.
\end{itemize}

\textbf{Contacts}
\begin{itemize}
	\item \textbf{Phone:} 869363208
	\item \textbf{Email:} lt.tutkus7@gmail.com
\end{itemize}

\textbf{More information}
\begin{itemize}
	\item \textbf{Birth date}: 1992 - 10 - 19
	\item \textbf{Nationality}: Lithuanian
\end{itemize}
\vfill

Vilnius \ \  2015
\end{center}



\clearpage

\section{Personal qualities}
\begin{itemize}
	\item In team work I always try my best in finding problems solution
	\item I can easily adapt in various situations and  becouse of I'm stubborn I can overcome all problems in work.
	\item I'm diplomatic and doing my best to improve from any given remarks or critics.
	\item I'm slow at a times so it would be more useful to give precise tasks.
	\item I'm open to new technologies and attempting to move forward in various situations.
\end{itemize}

\section{Education}
\textbf{2000-2012} \\
Anykščių Jono Biliūno gimnazija. Best known areas: biology, mathematics, physics, informatics. \\

\textbf{2012 - 2016} \\ 
Student of Vilnius University Mathematic and Informatics faculty, specialty - bioinformatics.

\textbf{Bachelour} \\
Theme name: DNR replication processivity factors analysis.
Executive: Darius Kazlauskas\\
Done in: VU biotechnology institution, bioinformatics section. 

\textbf{Knowledge from bachelour studies}
\begin{itemize}
	\item Programming system engineer, website development(HTML, CSS, JS, PHP);
	
	\item Programming languages: C++, C\#, Python, Game development and programs testing with Makefiles;
	
	\item Molecular movement and interactions, formulating these process into differential mathematics equation and finding solutions, performing statistical experiments.
\end{itemize}

\clearpage

\vspace{8cm}


\section{Work skills}
\textbf{2015/01/01 iki 2015/05/31} \\
Practics in biotechnology institution from second to fourth course. Also spend half year working there as a Python programmer.

\vspace{0.5cm}
\textbf{2016/02/01 iki 2015/03/01} \\
Game developer in "Nordcurrent" company. Learned much about objectiver orientated C++ programming also created two simple games.
\vspace{0.5cm}


\section{Basic skills}
\textbf{Languages}
\begin{enumerate}
	\item English - C1 level speaking and B2 level writing. 
	\item German - overall B1 level.
\end{enumerate}

\textbf{IT}
\begin{enumerate}
	\item C++ various programs creation in University and some in leisure time also practics. (2 years).
	
	\item Creating games with unity, C\# programming language (1 year).
	
	\item C, Java programming languages basics(less than 1 year).
	
	\item Python, Perl programming languages (3 years).
	
	\item HTML, CSS, PHP, JS (1 year).
\end{enumerate}

\textbf{Other}
\begin{enumerate}
	\item Vim in Linux environment, Visual Studio in Windows.
	\item Worked a lot with programms like Unity, R, Mapple, Latex.
	\item Practics in music creation with Magix Music Maker.
\end{enumerate}

\clearpage

\section{Hobbies}
\textbf{Sport}
\begin{itemize}
	\item Basketball
	\item Judo
	\item Running
	\item Tennis
\end{itemize}

\textbf{Leisure time}
\begin{itemize}
	\item Game creation
	\item Playing PC games(FPS, RPG, MOBA)
	\item Read action, detective or other type intresting books.
	\item Play desk games (Chess).
\end{itemize}

\textbf{Music}
\begin{itemize}
	\item Playing with guitar and piano.
	\item Create music with electric piano.
\end{itemize}

\end{document}
